\chapter{Related work}
\label{ch:related_work}
\todo{should be preliminaries?}

\section{Natural language processing}
\label{sec:natural_language_processing}
For a review check~\cite{chowdhury2003natural}.


\section{Automated customer service}
\label{sec:automated_customer_service}
When customers are unable to solve some product related problem they can turn to the customer service. ...goals of customer service...
Ideally, automation can improve customer satisfaction by responding quickly.
Another benefit is that the automation can be cheaper.
It is important to keep customer satisfaction in mind. \\

Customer service employees observe that a useful case for a bot would be helping customers with time critical problems.
Examples of this could be an offline phone or cancelling a flight.
Typical problems observed are where the customer service redirects the customer to a knowledge base article.
Including this article in a chat seems of limited use since it hides the document structure. \\

Knowledge base is often unstructured.
A typical problem is to include this information in the support.
According to IBM automating customer service is the future~\cite{schneider2017ai}.
They call it ``conversational AI''.\\

Review~\cite{braun2017}

\subsection{Startups}
\label{subsec:startups}
That NEEDLE (\url{http://www.thatneedle.com}) provide a deep text analysis API. It seems much more involved to get it running (and keep it running) on dynamic data. \todo{clarify this}

Digital Genius \url{https://www.digitalgenius.com} is also an AI customer service tool.
Interaction with the tool has been used by BMW to plan test drives with customers.
Pricing is aimed at big companies it seems.
Watson can be set up by user instead of by company (citation needed, mentioned in TechCrunch video). \\

The problem of automating customer service has already been deployed at other telecommunication companies according to Digital Genius.
The company is also working on measuring parameters from communication with the customer, like how price sensitive the customer is and openness to innovation.
These parameters can be used to change communication with the communication.
For example, if a customer ask many questions which indicate he knows about technology then answers could use this fact.

\subsection{Google Next}
\label{subsec:google_next}
Google Cloud Next (\url{https://youtu.be/bRnN4pBAsfc}) list seven social media customer feedback channels.
They call customer service requests \textit{touchpoints}.
They call a conversation between customer and customer service a \textit{customer journey}.
For these conversations they classify whether a touch point has high priority.
The interpretation can be used to route the customer.
The Google Next presentation focus on the speech interpretation and NLP.
Cloud Speech allows streaming.
Not all e-mails require a response.
Simple NLP is able to solve these e-mails automatically.
Drawback of most ML solutions is that you need a large corpus of training data. \\


\subsection{Watson}
IBM Watson is a well-known question answering computer system.
In 2011 the system got famous for winning from humans in the \textit{Jeopardy!} quiz show.
The show asked the questions to Watson in natural language.
For this they used a supercomputer of which the building was in progress in 2004~\cite{bhanot2004qcd}.
The Watson Assistant aid customers by capturing their \textit{intents} and helping them by choosing the correct dialog flow.
An example of an intent is booking a flight or answering a question.
The intents are specified by a intent name, description and user examples.
For example, a Watson sample system uses 23 examples to detect whether a customer wants to locate a physical store location or address.  \\

Compared to general NLP solutions Watson excels at solving ambiguity in conversations and highly domain specific problems \todo{citation needed}

Watson can be applied in specific domains by teaching it domain language via the Watson Knowledge Suite. \\





Engati (\url{https://www.engati.com}) integrate with various messaging and CRM platforms.
Nice thing about Watson is that they clearly focus on the NLP, conversation and user set-up.
The integration is for the users.

Drift (\url{https://www.drift.com/})

\section{Question answering}
\label{sec:question_answering}
\todo{question answering introduction}

Real-life questions and answers occur in context.
To this end ``users generally prefer answers embedded in context''~\cite{lin2003makes}. \\

\url{https://www.ibm.com/blogs/research/2018/02/open-domain-qa}