\chapter*{Preface}
\label{ch:preface}

This master thesis is aimed to graduate for the Computer Science and Engineering master at Eindhoven University of Technology.
The project is carried out at Devhouse Spindle in Groningen.
The thesis concludes my education in Eindhoven.
I consider choosing this study as one of the best decisions of my life.
Getting good grades for assignments and exams was though, but grading was fair.
Teachers were always busy, but also always willing to help.
I would like to thank Nikolay Yakovets for being willing to guide the project and for the guidance during the project.
I appreciate the fact that Nikolay allowed me to choose a subject that does not directly aid him in his research.
Furthermore, I would like to thank Devhouse Spindle for allowing me to graduate at their company.
Little could be improved about the workplace, collegues and office in general.
I would like to thank my graduation tutor Jukka Koivunen for the guidance and helping me fix any bugs related to object-oriented code.
Thanks to colleagues for the relaxed work environment, the advices and for helping me fix bugs I would have been stuck on for many hours.

In general I would like to thank Rodger, Erik, Mark, Leon, Stan, Astrid, Sjors, Nol, Tom, Suzanne, Reggie, Imke, the student ice hockey team and the student rugby team, to help me getting through the study.
Finally, special thanks go out to my parents and siblings for motivating me to aim high.

% first report where parents did not even try to give feedback, still thanks for supporting me through all previous education

\vspace*{5mm}
Rik Huijzer

\today