\section{Search}
\label{sec:search}

The field of NLP is rapidly evolving due to the introduction of deep learning.
Systems which obtain state of the art (SOTA) accuracy are often surpassed within a few months.
A search is conducted to improve the accuracy of the existing systems.
The research for this part has not been systematic.
This is caused by the goal to improve accuracy.
The method for finding an improvement is based on coming up with `novel' approaches to improve accuracy.
After having such an `novel' approach the literature is consulted.
This search method relies on the assumption that papers have done their research and will provide proper related work.
This section will explain the considered ideas and related literature.

\subsection{Duplicate finding}
\label{subsec:duplicate_finding}
% clustering
A large part of communications with customers consist of answering questions.
Some questions will be duplicates, or in other words, some questions will have been asked and answered before.
Finding duplicate questions is the same as finding clusters in the data.
Another approach could be based on template responses used by customer support teams.
A classifier could be trained to come up with these template responses.

% semantic text similarity
Another approach to find duplicates is using semantic text similarity (STS).
STS is a NLP tasks focusing on finding sentences (or texts) having the same meaning.
It is a recurring task in the SemEval workshop.
Systems in this field obtain impressive results, however it would not help with the chosen task of intent classification.
Also, intent classification is more useful for the thesis than only knowing whether two sentences are the same.

\subsection{Using data}
\label{subsec:using_data}
According to~\citet{warden2018} it is more effective to get more training data than to apply better models and algorithms.
For conversational agents in company settings it is easy to get raw data.
This shifts the problem to applying to automatic data wrangling.
This is not further investigated since the data obtained from customers cannot be part of a public thesis.
Learning automatically from users is applied by some Microsoft chatbots.
Microsoft Tay famously started to learn offensive language from users and has been shut down as a result.
In China Microsoft has had a more successful release of XiaoIce.
XiaoIce is optimized for ``long-term user engagement''~\citep{zhou2018design}.
Engagement is achieved by establishing an emotional connection with the user.
This system which is created by a research lab and being used by 660 million users does not automatically use the data to learn.
The authors manually optimize the engagement of the system.
From this it is concluded that reinforcement learning and automatic data wrangling are not yet feasible approaches to increase accuracy.

\subsection{Kaggle}
\label{subsec:kaggle}
Kaggle (\url{https://www.kaggle.com}) is a well-known site in the machine learning domain.
On this site a framework exists where datasets can be published.
The site, along other things, shows statistics, a comments section and a scoreboard.
It is famous for hosting `competitions', where the person or team obtaining the highest accuracy for some task gets price money from the dataset hoster.
Kaggle provides a way for machine learning enthusiasts to communicate.
People who obtain top 20 high scores on difficult tasks tend to explain their pipeline in a blogpost.
Research papers tend to focus on designing the best deep learning architectures.
The Kaggle explanations are valuable sources for learning how to get the most out of the architectures.

One such post~\citep{kumar2018} uses three embeddings, namely Glove, FastText and Paragram.
The author argues that ``there is a good chance that they (the embeddings) capture different type of information from the data''.
This method is called boosting.
Predictions from the embeddings are combined by taking the average score.
A threshold is set to remove answers where the model is unsure.
This method could be used to improve performance for natural language understanding.
Running three systems in parallel does increase the training time, but the difference is not too large.
It would be interesting to test whether averaging can be replaced by a more involved calculation.
Meta-algorithms such as boosting, bagging and stacking are not investigated further since the improvement is expected to be insignificant.
% Complete meta-algorithm surveys like the work by~\citet{vanschoren2018meta} have only been skimmed through.

\subsection{Meta-learning}
\label{subsec:meta-learning}
Meta-learning is ``is the science of systematically observing how different machine learning approaches perform on a wide range of learning tasks, and then learning from this experience, or meta-data, to learn new tasks much faster than otherwise possible''~\citet{vanschoren2018meta}.
Few-shot learning aims to learn useful representations from a few examples.
In practise most intent classification systems use few examples, so few-shot learning is interesting to the research question.
This was also concluded by the IBM T. J. Watson Research Center~\citep{yu2018diverse}.
The authors show that their system outperforms other few-shot learning approaches.
They do not compare their system against natural language understanding solutions and conclude that their research should be applied to other few-shot learning tasks.
This implies that natural language understanding specific systems obtain higher accuracies.
Automatically tuning hyperparameters as done in TensorFlow's AutoML is based on the work by~\citet{andrychowicz2016learning}.
Industry claim that AutoML obtains 95\% of the accuracy of hand-tuning hyperparameters.
Another problem is that it does not scale well~\citep{jones2017}.
Transfer learning approaches like MAML~\citep{finn2017model} and Reptile~\citep{nichol2018reptile} could be useful for intent classification as well.
Different domains require different models.
Reptile seems interesting to be used to train a model on one domain and then be able to easily switch the model to other domains.
This would introduce a lot of complexity in the code.
More convenient would be using a model which works on all domains.

\subsection{Embeddings}
\label{subsec:embeddings}
Embeddings capture knowledge about language and use that for downstream tasks.
There appears to be a consensus about the timeline of embeddings evolution.
Glove~\citep{pennington2014} was superseded by FastText~\citep{joulin2016bag}.
The Facebook FastText embedding is aimed to be quick, allowing it to be used as a baseline.
With 157 languages (\url{https://fasttext.cc/}) it is a mutli-lingual model.
Another state-of-the-art and easy to implement embedding is the universal sentence encoder~\citep{cer2018universal}.
The word `universal' denotes that the system has used a supervised training task which has been chosen such that the embeddings generalize to downstream tasks.
Not only Google, but also Microsoft research is working on multi-task learning~\citep{subramanian2018learning}.
These embeddings are not enough to improve on existing systems, since Rasa is using the universal sentence encoder~\citep{wiese2018}.
One step further would be to let the model decide what embedding it wants to use~\citep{kiela2018dynamic}.
A caveat is the fact that one then needs to implement multiple embeddings (even when the model decides that one embedding is the best).
